analysis

### 2019-11-23 explore.Rmd
added netmeta results

@@

PM_mv1 <- rma.mv(yi, vi, 
                    mods = ~ spray_management, 
                    method="ML",
                    random = list(~ spray_management | trial, ~1 | id), 
                    struct="UN", data=datPM)

@@

>>>>

```{r}
control <- datPM %>% 
   filter(spray_management == "control") %>% 
group_by(trial) %>% 
summarize(sev_control = mean(PM_final_severity))

control %>% 
   ggplot(aes(sev_control))+
   geom_histogram()

datPM2 <- left_join(control, datPM) %>% 
   filter(year != 2019)

datPM2 %>% 
   ggplot(aes(spray_management, yi, size = 1/vi, color = sev_control))+
   geom_jitter(width = 0.1)+
   facet_wrap(~year)

datPM2 %>% 
   filter(spray_management == "control") %>% 
   ggplot(aes(row_spacing, yi, size = 1/vi, color = sev_control))+
   geom_jitter(width = 0.1)

@@

PM_mv1 <- rma.mv(yi, vi, 
                    mods = ~ spray_management, 
                    random = list(~ spray_management | trial, ~1 | id), 
                    struct="UN", data=datPM2)

@@

```{r}
library(netmeta)

datPM3 <- datPM2 %>% 
   group_by(trial, spray_management, n) %>% 
      summarize(yi_mean = mean(yi), 
             vi_mean = mean(vi)) %>% 
   ungroup()

PM_con <- pairwise(treat = spray_management,
                  n = n,
                  mean = yi_mean,
                  sd = sqrt(vi_mean),
                  studlab= trial,
                  data = datPM3, 
                  sm="MD")

```{r}
net_con <- netmeta(TE, 
                seTE, 
                treat1, 
                treat2, 
                studlab, 
                data=PM_con, 
                sm="MD")

summary(net_con)
```

```{r}
forest(net_con, reference.group = 4,
       rightcols=c("effect", "ci", "Pscore"),
       rightlabs="P-Score", small.values = "bad")
```

```{r}
netrank(net_con, small.values = "bad")
```

```{r}
netgraph(net_con, 
         plastic = FALSE,
         col = "orange",
         thickness =  "number.of.studies",
         points = FALSE, 
         col.points = "black", 
         cex.points = 1,
         number.of.studies = TRUE,
         cex.number.of.studies = 1,
         col.number.of.studies = "black",
         bg.number.of.studies = "orange",
         multiarm = FALSE,
         col.multiarm = "lightblue",
         pos.number.of.studies = 0.5)
```

```{r}
netleague(net_con)
```

```{r}
decomp.design(net_con)
```

```{r}
netsplit(net_con)
```
```{r}
nm1 <- netmeasures(net_con)

plot(nm1$meanpath, nm1$minpar, pch="",
     xlab="Mean path length", ylab="Minimal parallelism")
text(nm1$meanpath, nm1$minpar, names(nm1$meanpath), cex=0.8)
```
